---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# 2021 Summer Institute in Computational Social Science

<!-- badges: start -->
<!-- badges: end -->

Anotações sobre o [2021 Summer Institute in Computational Social Science](https://sicss.io/2021/fgv-dapp-brazil/).


## Anotações prévias

- [X] [Day 1: Introduction and Ethics](notes/Day_1-Introduction_and_Ethics/README.md)

- [X] [Day 2: Collecting Digital Trace Data](notes/Day_2-Collecting_Digital_Trace_Data/README.md)

- [x] [Day 3: Automated Text Analysis](notes/Day_3-Automated_Text_Analysis/README.md)

- [x] [Day 4: Surveys in the Digital Age](notes/Day_4-Surveys_in_the_Digital_Age/README.md)

- [x] [Day 5: Mass Collaboration](notes/Day_5-Mass_Collaboration/README.md)

- [ ] [Day 6: Experiments](notes/Day_6-Experiments/README.md)

## Leitura do livro *bit by bit*

```{r eval=FALSE, include=FALSE, results='asis'}
library(magrittr, include.only = "%>%")
url <- "https://www.bitbybitbook.com/en/1st-ed/preface/"

links <- rvest::read_html(url) %>% 
  rvest::html_node(xpath = '//*[@id="wrapper"]/nav/div[3]/ul') %>% 
  rvest::html_nodes("a") %>% 
  rvest::html_attr('href') 

lido <- rep(TRUE, 6)

falta_ler <- rep(FALSE, length(links) - length(lido))

leitura <- c(lido, falta_ler)

links %>%
  tibble::as_tibble() %>%
  dplyr::mutate(
    nome = stringr::str_remove_all(value, "/en/1st-ed/|/$"),
    link = paste0("https://www.bitbybitbook.com", value),
    md = glue::glue("[{nome}]({link})"),
    assistido = leitura,
    md = dplyr::case_when(
      assistido == TRUE ~ glue::glue("- [x] {md}"),
      assistido == FALSE ~ glue::glue("- [ ] {md}")
    )
  ) %>%
  dplyr::pull(md)


```

